# balanceHD

Estimation of average treatment effects in high dimensions via approximate residual balancing, as proposed by Athey et al. (2016). Fork of Stefan Wager's original package with some convenience functions + continued development using alternative nuisance function estimators.

To install this package in R, run the following commands:

```{r, eval = FALSE}
library(devtools)
install_github("apoorvalal/balanceHD")
```

This package currently works with three optimizers: `mosek`, `pogs`, and `quadprog`.
Mosek is a commercial interior point solver,
pogs is a first-order optimizer, based on ADMM, while
quadprog is a standard `R` optimization library.
In general, we achieved best performance with mosek, and
recommend trying optimizers in the order listed above.
We found pogs to be somewhat slower than mosek on the problems
we tried. (Note that we offer two solution strategies based on pogs: `pogs` and
`pogs.dual`. We usually recommend the former, except when p is much larger than n.)
Finally, quadprog performors well on small problems, but can be much
slower for larger problems.

In terms of availability, the optimizer quadprog is easiest to access,
and is available directly from CRAN. Pogs needs to be installed separately,
but is still free. To install pogs, simply install one of the pre-compiled
binaries available from the project [repository](https://github.com/foges/pogs);
see [this page](https://github.com/foges/pogs/blob/master/src/interface_r/README.md)
for furhter instructions.
Finally, mosek is a commercial solver; however, academic
[licenses](https://www.mosek.com/resources/academic-license) are available for free.
One mosek has been installed, we call into it using the R package Rmosek.

Example usage:

```{r}
set.seed(42)
library(balanceHD)

n = 400; p = 1000
tau = 7
nclust = 10
beta = 2 / (1:p) / sqrt(sum(1 / (1:p)^2))
# cluster assingment
clust.ptreat = rep(c(0.1, 0.9), nclust / 2)
cluster.center = 0.5 * matrix(rnorm(nclust * p), nclust, p)
cluster = sample.int(nclust, n, replace = TRUE)
X = cluster.center[cluster, ] + matrix(rnorm(n * p), n, p)

W = rbinom(n, 1, clust.ptreat[cluster])
Y = X %*% beta + rnorm(n, 0, 1) + tau * W

# bad
naive.ate(X, Y, W)
```

## main function

```{r}
library(tictoc)

tic()
tau.hat = residualBalance.ate(X, Y, W, estimate.se = TRUE, optimizer = "mosek")
toc()

print(paste("true tau:", tau))
print(paste("point estimate:", round(tau.hat[1], 2)))
print(paste0(
  "95% CI for tau: (", round(tau.hat[1] - 1.96 * tau.hat[2], 2),
  ", ", round(tau.hat[1] + 1.96 * tau.hat[2], 2), ")"
))
```

## alternate optimizers

```{r}
tic()
tau.hat = residualBalance.ate(X, Y, W, estimate.se = TRUE, optimizer = "quadprog")
toc()

print(paste("true tau:", tau))
print(paste("point estimate:", round(tau.hat[1], 2)))
print(paste0(
  "95% CI for tau: (", round(tau.hat[1] - 1.96 * tau.hat[2], 2),
  ", ", round(tau.hat[1] + 1.96 * tau.hat[2], 2), ")"
))
```

POGS is good for big problems but takes some setup on linux.

```{r}
tic()
tau.hat = residualBalance.ate(X, Y, W, estimate.se = TRUE, optimizer = "pogs")
toc()

print(paste("true tau:", tau))
print(paste("point estimate:", round(tau.hat[1], 2)))
print(paste0(
  "95% CI for tau: (", round(tau.hat[1] - 1.96 * tau.hat[2], 2),
  ", ", round(tau.hat[1] + 1.96 * tau.hat[2], 2), ")"
))
```

## Standard methods

### AIPW

Default elastic net for both outcome model and pscore.

```{r}
ipw.ate(X, Y, W, estimate.se = TRUE)
```

use grf for pscore

```{r}
ipw.ate(X, Y, W, prop.method = "randomforest", estimate.se = TRUE)
```

### IPW

```{r}
ipw.ate(X, Y, W, fit.method = "none", estimate.se = TRUE)
```

### OM

```{r}
elnet.ate(X, Y, W, estimate.se = TRUE)
```

### double lasso

```{r}
twostep.lasso.ate(X, Y, W, estimate.se = TRUE)
```




#### References
Susan Athey, Guido Imbens, and Stefan Wager.
<b>Approximate Residual Balancing: De-Biased Inference of Average Treatment Effects in High Dimensions.</b>
2016.
[<a href="http://arxiv.org/pdf/1604.07125.pdf">arxiv</a>]
